---
title: "Introduction to R"
---

This course provides a brief introduction to R, a statistical programming language for data science that is well suited to geographic data analysis and reproducible analysis and modelling to support evidence-based transport planning.

# Location

The lecture is located on Level 8 of the Worsley Building.
As shown below, that is around a 10 minute walk from ITS.
Ensure that you set-off on time, e.g. 08:30, to allow plenty of time to get lost, find the building, find the room and get set up before the lecture at 09:00.

```{r}
#| message: false
library(osmextract)
library(tidyverse)
```


```{r}
#| eval: false
west_yorkshire = oe_get(place = "West Yorkshire", layer = "multipolygons")
worsley_building = west_yorkshire %>%
  filter(name == "Worsley Building")
sf::write_sf(worsley_building, "worsley_building.geojson")
walking_route = stplanr::route(from = "institute for transport studies leeds",
                               to = "worsley building leeds",
                               route_fun = stplanr::route_osrm
                               )
sf::write_sf(walking_route, "walking_route.geojson")
```

```{r}
worsley_building = sf::read_sf("worsley_building.geojson")
walking_route = sf::read_sf("walking_route.geojson")
library(tmap)
tmap_mode("view")
tm_shape(walking_route) +
  tm_lines(lwd = 5) +
  tm_shape(worsley_building) +
  tm_polygons() +
  tm_view(set.zoom.limits = c(15, 17)) +
  tm_basemap(server = leaflet::providers$OpenStreetMap)
```

```{r}
#| eval: false
#| echo: false

sf::sf_use_s2(TRUE)
worsley_surroundings_500m = sf::st_buffer(worsley_building, dist = 1000)
sf::sf_use_s2(FALSE)
nearby_buildings = west_yorkshire[worsley_surroundings_500m, , op = sf::st_within]

```

